
\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}
\newcommand{\header} [1] {
    \vspace{2mm}
    {\hspace*{-18pt}\vspace*{7pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
    \vspace{1mm}
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Marco Antonio Gonzalez Junior}}                \\
    \vspace{2.5pt}
    m@rco.sh $\cdot$ +55 (11) 91577-7715 $\cdot$ São Paulo, Brazil  \\
    \vspace{2.5pt}
    https://linkedin.com/in/marcoantoniogonzalezjunior              \\
\end{center}

%==== Professional Summary ====%
\header{Professional Summary}
Seasoned Solutions Architect with over 15 years of experience in designing and implementing large-scale systems and cloud-native solutions. Proven track record of leading cross-functional teams and delivering innovative, high-performance, and scalable solutions for the finance, retail, and e-commerce sectors. Strong expertise in AWS cloud architecture, microservices, and data-driven decision-making. Adept at aligning technology with business goals and driving continuous improvement across development teams.

%==== Education ====%
\header{Education}
\textbf{Faculdade de Informática e Administração Paulista}\hfill São Paulo\\
MBA Data Science \hfill 2015 $\sim$ 2016\\
\vspace{1mm}
\textbf{Faculdade Impacta de Tecnologia}\hfill São Paulo\\
BS Information Systems \hfill 2011 $\sim$ 2015\\
\vspace{1mm}
\textbf{Universidade Federal de São Carlos}\hfill São Carlos\\
BS Materials Engineering \hfill 1996 $\sim$ 2000\\


%==== Skills ====%
\header{Skills}
\vspace{1mm}
\begin{tabular}{ l l }
    Cloud Architecture & AWS, GCP, Azure, Microservices, Serverless, Well-Architected \\
    Programming & Python, TypeScript, Java, Ruby, Flutter, Shell Scripting \\
    Web & React, Next.js, Astro, Rails, Django, Svelte \\
    Data & Data Wrangling, Big Data, Machine Learning, TensorFlow, PyTorch \\
    Integration & REST, GraphQL, gRPC, Legacy Systems \\
    DevOps & CI/CD, Docker, Kubernetes, Jenkins, Terraform \\
\end{tabular}

%==== Certifications ====%
\header{Certifications}
\textbf{Cloud Certifications} \\
AWS Certified Solutions Architect, Data Engineer, Developer \& Cloud Practitioner. \\
\vspace{0.5mm}
\textbf{AI \& Data Science Certifications} \\
AWS Certified Machine Learning (Specialty), Machine Learning Engineer \& AI Practitioner. IBM AI Developer \& Engineering (Professional), Stanford Machine Learning \& Deep Learning Specialization.

%==== Experience ====%
\header{Experience}
\textbf{IBM} \hfill \textit{Jul 2022 $\sim$ Sep 2024} \\
Senior Solutions Architect \\
\vspace{-3mm}
\begin{itemize}
\setlength\itemsep{-1mm}
    \item Delivered AI-driven solutions by implementing and optimizing IBM WatsonX features for clients in finance and retail, enhancing operational efficiency and customer experience.
    \item Architected cloud-native AI models to support scalable, high-availability systems, integrating WatsonX capabilities with existing infrastructure for seamless performance.
    \item Provided strategic AI consultations, guiding clients on best practices for machine learning, NLP, and analytics integration to maximize data and technology investments.
    \item Led AI training initiatives, enabling teams to leverage WatsonX tools for predictive analytics, customer insights, fraud detection, and personalized retail experiences.
\end{itemize}
\vspace{-2mm}
\textbf{banQi} \hfill \textit{Jun 2019 $\sim$ Jul 2022} \\
Senior Solutions Architect \\
\vspace{-3mm}
\begin{itemize}
\setlength\itemsep{-1mm}
    \item Unified system architecture, reducing downtime by 40\% and improving performance by 25\%.
    \item Introduced microservices architecture, boosting deployment frequency by 50\%.
    \item Led platform engineering efforts, optimizing infrastructure and automating workflows.
\end{itemize}
\vspace{-2mm}
\textbf{Petlove} \hfill \textit{May 2015 $\sim$ Jun 2019} \\
Tech Lead \\
\vspace{-3mm}
\begin{itemize}
\setlength\itemsep{-1mm}
    \item Architected and led the development of a membership project, increasing monthly revenue by 30%.
    \item Improved repurchase rates by 500\% through process optimization in the ERP system.
\end{itemize}
\vspace{-2mm}
%==== Additional Experience ====%
\header{Past Experiences}
\textbf{Jüssi} | Solutions Architect \hfill \textit{Nov 2012 $\sim$ May 2015} \\
\textbf{Editora Abril} | Senior Software Developer \hfill \textit{Sep 2008 $\sim$ Nov 2012} \\
\textbf{Western Union} | Senior Software Developer \hfill \textit{May 2005 $\sim$ Nov 2008} \\
\textbf{Toyota} | Software Developer \hfill \textit{May 2003 $\sim$ Apr 2005} \\

\end{document}
