\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}
\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\newlength{\sectionindent}
\setlength{\sectionindent}{-0.4in} % Negative value shifts content left

% Update the header command to apply this indent
\renewcommand{\header}[1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Marco Antonio Gonzalez Junior}}                \\
    \vspace{2.5pt}
    m@rco.sh $\cdot$ +55 (11) 91577-7715 $\cdot$ São Paulo, Brazil  \\
    \vspace{2.5pt}
    https://linkedin.com/in/marcoantoniogonzalezjunior              \\
\end{center}

%==== Professional Summary ====%
\header{Professional Summary}
\sloppy
My engineering journey began at age 11, igniting a passion for problem-solving and continuous learning that has driven over two decades of professional development. I evolved from a dedicated developer into a seasoned solutions architect and technical leader, mastering diverse programming languages from Assembly and C/C++ to modern TypeScript and Python. This polyglot programming foundation, combined with comprehensive full-stack and DevOps expertise, enabled me to architect scalable solutions across multiple technology stacks while developing deep expertise in cloud platforms, web standards, and Linux systems. As a result-oriented technical leader, I consistently tackle complex engineering challenges while fostering collaborative environments and knowledge sharing.

\vspace{2mm}

Since 2014, I have been developing artificial intelligence and machine learning solutions, delivering impactful applications across diverse industries including classification algorithms for marketing optimization, recommendation systems for retail platforms, predictive forecasting for supply chain operations, and anomaly detection for fraud prevention. Over the past three years, I strategically pivoted to specialize in generative AI, investing extensively in advanced training to build deep expertise in this transformative technology. I now work extensively with foundation model architectures, implementing continued pre-training and advanced fine-tuning techniques that achieve specialized domain expertise, while building standalone RAG systems and sophisticated hybrid architectures that combine retrieval and fine-tuning approaches for enhanced capabilities.

\vspace{2mm}

My current expertise encompasses advanced agentic AI systems, where I implement sophisticated multi-agent architectures. I develop tool-using agents with function calling capabilities and external system integration through MCP, design complex sub-agent architectures for parallel task decomposition, and implement long-term memory systems with knowledge graph integration. Simultaneously, I revolutionize development workflows through mastery of AI-assisted coding tools, leveraging Claude Code with sub-agents and advanced IDE integrations across VSCode with GitHub Copilot, Cursor AI, and Kiro. I actively explore emerging AI paradigms including fully autonomous systems, advanced context engineering techniques, and AI-native development methodologies that fundamentally reimagine software creation through intelligent automation.

\fussy
\vspace{2mm}

%==== Education ====%
\header{Education}
\vspace{1.5mm}
\textbf{Faculdade de Informática e Administração Paulista}\hfill São Paulo\\
MBA Data Science \hfill 2015 | 2016\\
\vspace{1.5mm}
\textbf{Faculdade Impacta de Tecnologia}\hfill São Paulo\\
BS Information Systems \hfill 2011 | 2015\\
\vspace{1.5mm}
\textbf{Universidade Federal de São Carlos}\hfill São Carlos\\
BS Materials Engineering \hfill 1996 | 2000\\
\vspace{2mm}

%==== Skills ====%
\header{Skills}
\vspace{2mm}
\begin{tabular}{ @{}l l }
	Engineering background:               & Scientific method, Calculus, Algebra, Physics, Statistics        \\[0.5ex]
	Cloud Computing:                      & Amazon Web Services, Azure, Google Cloud Platform                \\[0.5ex]
	Architecture Governance:              & Decision Frameworks, Technical Debt Management, Review Processes \\[0.5ex]
	Enterprise Integration:               & Integration Patterns, API Gateways, Message Brokers, ESB,        \\
                                        & Event Sourcing, CQRS, Saga Pattern, Service Mesh, Message Queues \\[0.5ex]
  Architecture Approaches:              & Domain-Driven Design, Event-Driven Architecture, Microservices,  \\
                                        & Service-Oriented Architecture, Hexagonal Architecture            \\[0.5ex]
	DevOps:                               & Docker, Kubernetes, Terraform, Packer, GitHub Actions, ArgoCD,     \\
	                                      & Helm, Jenkins, Ansible, GitOps Workflows                         \\[0.5ex]
	CI/CD Pipelines:                      & Advanced Deployment Strategies, Pipeline Security, Build Automation \\[0.5ex]
	Observability:                        & Prometheus, Grafana, Jaeger, OpenTelemetry, Datadog, ELK Stack,   \\
	                                      & Grafana LGTM Stack, Distributed Tracing, SLOs/SLIs, Error Budgets \\[0.5ex]
	Performance Engineering:              & Load Testing, Caching Patterns, Distributed Systems Optimization \\[0.5ex]
	API Development:                      & RESTful Architecture, GraphQL, gRPC, WebSockets, API Gateway,     \\
	                                      & OpenAPI/Swagger, Security, Rate Limiting, Versioning            \\[0.5ex]
	Web Development:                      & Frontend (HTML5, CSS3, JavaScript), Backend, Performance Optimization, \\
	                                      & SEO, Responsive Design, Web Accessibility, Progressive Web Apps  \\[0.5ex]
	Web frameworks:                       & React, Next.js, Rails, Django, Flask, Express, Svelte           \\[0.5ex]
	Programming languages:                & TypeScript, Python, Go, Ruby, Java, Flutter, C++               \\[0.5ex]
	Databases:                            & Relational, Key-Valued, Columnar, Graph and Document oriented   \\[0.5ex]
	Data Science:                         & Data Wrangling, Analysis, Visualization, Big Data, Streaming      \\
	                                      & Architectures, Statistical Modeling, ETL Pipelines, Data Lakes        \\[0.5ex]
	Machine Learning:                     & Algorithm Design, Model Optimization, Feature Engineering, Evaluation \\[0.5ex]
	Deep Learning:                        & PyTorch, TensorFlow, Keras, Neural Networks, Computer Vision, NLP,       \\
	                                      & Transformers                                                     \\
\end{tabular}
\vspace{6mm}

%==== Coursework ====%
\header{Certifications}
\vspace{1mm}

\textbf{Amazon Web Services (AWS)}          \hfill       \\
Certified Solutions Architect Professional  \hfill 2025  \\
Certified Machine Learning Engineer         \hfill 2024  \\
Certified Machine Learning - Specialty      \hfill 2024  \\
Certified AI Practitioner                   \hfill 2024  \\
Certified Solutions Architect Associate     \hfill 2022  \\
Certified Developer                         \hfill 2022  \\
Certified Cloud Practitioner                \hfill 2022  \\

\vspace{1mm}
\textbf{Stanford University and DeepLearning.AI} \hfill      \\
Machine Learning Specialization                  \hfill 2024 \\
Deep Learning Specialization                     \hfill 2024 \\

\vspace{1mm}
\textbf{IBM}                          \hfill      \\
IBM AI Engineering Professional       \hfill 2024 \\
IBM AI Developer Professional         \hfill 2024 \\
Generative AI for Software Developers \hfill 2024 \\

\vspace{1mm}
\textbf{University of Alberta}                  \hfill      \\
Software Design and Architecture Specialization \hfill 2024 \\

\vspace{1mm}
\textbf{University of Michigan}       \hfill      \\
Statistics with Python Specialization \hfill 2019 \\

\vspace{1.0mm}
\textbf{Stanford University} \hfill      \\
Machine Learning (CS229)     \hfill 2017 \\

\vspace{1.0mm}
\textbf{University of California, San Diego}\hfill \\
Big Data Specialization \hfill 2016 \\

\vspace{1.0mm}
\textbf{University of Washington}\hfill \\
Machine Learning Specialization \hfill 2016 \\

\vspace{1.0mm}
\textbf{Johns Hopkins University}\hfill \\
Data Science Specialization \hfill 2015 \\

\vspace{1.0mm}
\textbf{University of Illinois at Urbana-Champaign} \hfill      \\
Data Mining Specialization                          \hfill 2015 \\

\vspace{1.0mm}
\textbf{Linux Professional Institute} \hfill      \\
LPI 101, LPI 102                      \hfill 2010 \\

\vspace{1.0mm}
\textbf{Sun Microsystems}\hfill \\
Certified on the Java Platform: SCJA, SCJP, SCJD, SCWCD, SCBCD, SCDJWS, SCEA \hfill 2008\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}
%======== Capco ========% 
\textbf{Capco}                                                      \hfill São Paulo              \\
\textit{Solutions Architect - Artificial Intelligence}               \hfill Sep 2024 | current    \\
\vspace{1mm}
As a Solutions Architect specialized in artificial intelligence, I developed and optimized foundation models through continued pre-training and fine-tuning for specialized reasoning and domain expertise. I built both standalone RAG systems for dynamic data environments and hybrid architectures that combined retrieval and fine-tuning approaches for enhanced accuracy and capabilities. \\
My primary focus involved systematically modernizing legacy COBOL applications using knowledge graphs built on enterprise graph database platforms to map programming constructs and business logic patterns. This enabled automated translation to modern languages like Java or .NET while providing comprehensive documentation of previously undocumented legacy codebases.
Using AI orchestration frameworks, I implemented retrieval-augmented generation workflows that queried knowledge graphs for relevant transformation rules and architectural patterns, then provided this contextual information to large language models for accurate code translation and intelligent documentation generation. \\
This approach ensured consistent mapping of legacy business logic, maintained semantic equivalence across programming languages, and enabled organizations to reduce modernization timelines while preserving mission-critical business rules embedded in decades-old codebases. The result was unlocking significant value trapped in legacy systems while eliminating technical debt and reducing operational risk.
\newline



%======== IBM ========% 
\textbf{IBM}                                                      \hfill São Paulo              \\
\textit{Senior Solutions Architect}                               \hfill Jul 2022 | Sep 2024    \\
\vspace{1mm}
As a Consultant at IBM, I specialized in implementing and optimizing IBM WatsonX features for enterprise clients, delivering AI-driven solutions to meet business needs in the finance and retail sectors. My responsibilities included advising clients on best practices for integrating WatsonX's advanced machine learning, natural language processing, and analytics capabilities into cloud-native applications and solutions architecture. I collaborated with cross-functional teams to design and implement scalable AI strategies that enhanced operational efficiency, data-driven decision-making, and customer experience.
\newline
In this role, my main accomplishments were:
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{-1mm}
\item Led comprehensive consultations from discovery to deployment, designing cloud-native AI solutions that addressed industry-specific challenges in finance and retail.
\item Architected and implemented scalable WatsonX models within cloud-native environments to support high-availability systems and optimize performance in both sectors.
\item Developed solutions architectures to integrate WatsonX AI capabilities with existing cloud infrastructure, ensuring seamless functionality and security.
\item Provided clients with strategic recommendations on enhancing their AI and cloud strategies, enabling them to maximize the value of their data and technology investments.
\item Delivered training and knowledge transfers on leveraging WatsonX tools for predictive analytics, customer insights, and fraud detection in finance, and personalized shopping experiences in retail.
\end{itemize}
\vspace{-1mm}

%======== banQi ========% 
\textbf{banQi}                                 \hfill São Paulo             \\
\textit{Senior Solutions Architect}            \hfill Jun 2019 | Jul 2022   \\
\vspace{1mm}
As a Solutions Architect and Technical Lead, I led cross-functional collaboration with stakeholders to ensure that system architecture aligned with both the organization's strategic goals and the product vision. I unified architectural designs and drove technical decisions, ensuring scalability, sustainability, and efficiency throughout our systems. My work focused on delivering robust and effective solutions architecture, addressing complex business challenges while maintaining alignment with enterprise strategies.
\newline
In this role, my key responsibilities included:
\vspace{-2mm} 
\begin{itemize}
\setlength\itemsep{-1mm}
    \item Evaluating, adopting, and advocating for new technologies to drive continuous innovation in architecture and development practices.
    \item Leading the design, development, and deployment of technical solutions that met high standards of performance, security, availability, and data integrity.
    \item Overseeing platform engineering efforts to ensure that infrastructure and tooling supported scalability, automation, and efficient development workflows.
    \item Recruiting and mentoring technical talent, fostering a culture of excellence and growth within the organization.
\end{itemize}
\vspace{-1mm}

%======== Petlove ========%
\textbf{Petlove}                               \hfill São Paulo             \\
\textit{Tech Lead}                             \hfill May 2015 | Jun 2019   \\
\vspace{-3mm}
\begin{itemize}
	\setlength\itemsep{-1mm}
	\item Biggest e-commerce of pet supplies in Brazil.
	\item Architect and lead the development of the prime membership project which turned to achieve 30\% of the monthly revenue and increased the repurchase rate per year by 500\%.
	\item Responsible for understanding and mapping all the company internal processes related to the ERP system. This effort\textquotesingle{}s goal was to upgrade it in order to be able to create multiple WMS, allowing the company to expand their market to other country states. Lead all the technical details involved.
	\item Technical leadership and management of the Business Intelligence team. Responsible for research and adoption of cutting edge technologies related to big data.
	\item Lead the definition and creation of an internal supply chain project. Working together with the procurement department in order to automate, manage and optimize the inventory and automate the purchases from suppliers.
\end{itemize}
\vspace{-1.5mm}

%======== Jüssi ========%
\textbf{Jüssi}                                 \hfill São Paulo         \\
\textit{Solutions Architect} \hfill Nov 2012 | May 2015                 \\
\vspace{-3mm}
\begin{itemize}
	\setlength\itemsep{-1mm}
	\item Digital marketing and performance industry, medium sized.
	\item Work together with Sales and Product teams to turn ideas into software solutions.
	\item Lead the Facebook Marketing Partner membership, working closely with the Facebook Engineering team to architect and deliver digital marketing solutions to big companies.
	\item Lead the Google Partner membership, cooperating with Google Engineers to architect and deliver Google Adwords and Google Shopping automation solutions.
\end{itemize}
\vspace{-2mm}

\textbf{Editora Abril} \hfill São Paulo\\
\textit{Senior Software Engineer} \hfill Sep 2008 | Nov 2012\\
\vspace{-3mm}
\begin{itemize}
	\setlength\itemsep{-1mm}
	\item Culture and entertainment industry, big sized.
	\item Development and support internal and external legacy projects, such as a project called Veja SP, an huge catalog and guide for restaurants, nightlife, cinema, etc. And a big internal project for content and assets management through the whole company.
\end{itemize}
\vspace{-2.5mm}

\header{Past Experiences}
\vspace{1.5mm}
\begin{tabular}{ @{}l l }
    Serasa Experian & Enterprise Architect \\
    Western Union & Senior Software Engineer \\
    Toyota do Brasil & Software Engineer    \\
    Wdotnet Internet & Owner    \\
    Flyever Electronics & Software Engineer \\
\end{tabular}
\vspace{1.5mm}

\end{document}